### 2019-07-09 manuscript/introduction.tex
updated some text for the additional models

Species accumulate across the tree of life at different rates. 
One possible explanation for this phenomenon is that the various traits or character states of species differentially affect rates of diversification. 
Dramatic increases in phylogenetic and phenotypic data and methodological advances have greatly accelerated the search for traits that influence diversification traits.
Nevertheless, identifying focal traits associated with rates of speciation and extinction remains a challenge \citep[\eg][]{maddison_2015, rabosky_2015, moore_2016, fitzjohn_2009, goldberg_2012, beaulieu_2016, rabosky_2017}. 
One difficulty is that speciation and extinction likely do not depend on a single trait, so the biological and environmental contexts in which traits occur can lead to complex interactions that affect lineage diversification \citep{beaulieu_2016, caetano_2018, herrera_2018}.
Consequently, examining the association of only one trait with diversification patterns can be misleading. 
Here, we embrace this challenge by jointly investigating two traits thought to influence speciation and extinction rates---ploidy level and breeding system---while allowing for their interactions and other confounding factors.
% E: We need a "Here, we..." here.  Otherwise, we've just told the reader "not one trait!" and then launch into one trait.

Polyploidization is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
The widespread prevalence of variation in ploidy has long been considered a salient feature of flowering plant lineages \citep{stebbins1938}. 
Increase in ploidy can alter many traits and affect a variety of evolutionary and ecological processes \citep{ramsey_2002, sessa_2019}.
%
Polyploids have been documented to have an overall lower diversification rate than diploids \citep{mayrose_2011, mayrose_2015}. 
Other studies, however, find common and numerous paleo-polyploidizations, including some preceding the emergence of highly diverse plant clades \citep{soltis_2014, landis_2018}, suggesting that whole genome duplications have played an important macroevolutionary role driving innovation and diversification in plants. 
Evidence of paleo-polyploidy within the genomes of diploid extant plants also implies pervasive diploidization, the return of polyploids to the diploid state, throughout the angiosperm phylogeny \citep{soltis_2015, dodsworth_2015}.
Our analyses re-examine the association between ploidy and lineage diversification by extending the approach of \citep{mayrose_2011, mayrose_2015} to include these additional processes.
We allow for transitions both toward and away from polyploidy, and for heterogeneous diversification within each ploidy level, for example if diploids have a relatively higher net diversification rate if they were ancestrally polyploid than if they had no polyploid ancestry.

@@

Polyploidy and self-fertilization are widely observed to be associated \citep{stebbins1950}.
There are several possible general explanations: whole genome duplication may facilitate the transition to selfing by masking inbreeding depression, self-fertilization may facilitate polyploidy establishment by avoiding the triploid bridge, or both selfing and polyploidy may be correlates of weedy or peripheral populations \citep{ramsey_1998, barringer2007, barrett2008, husband2008}.
Additionally, in RNase-based gametophytic SI systems, polyploidization alone directly causes the loss of SI \citep{stout1942, lewis1947}. %B: disclaimer: ceteris paribus statement omitted; polyploidization ordinarily causes SC because of the formation of heterodiploid pollen. On the background of deletion of S-locus, or with heterologous chromosome homozygosity at the S-locus may not do so. These, however, appear to be sufficiently rare that they are recovered perhaps twice in dicots: once (or twice) naturally, in sour cherry and it's close relative (Prunus), and once in a experimentally induced and selected synthetic pentaploid Solanum (which has not been replicated). Strictly speaking, this is a feature of non-self recognition systems of the kind found in RNase-based GSI.
In these systems, self-incompatibility is thought to occur because haploid self-pollen grains, with one S-allele at the locus controlling the SI response, are unable to detoxify the S-RNase produced by the same S-allele in the style \citep{kubo2010}.
The unreduced pollen of diploids, however, can contain two S-alleles expressed in pollen, which jointly gain the ability to detoxify the S-RNases produced by any maternal genotype \citep{entani1999, tsukamoto2005, kubo2010}.
Initial mutant individuals with pollen containing doubled haploid genomes are consequently capable of self-fertilization, with exceedingly few exceptions \citep{hauck_2002, nunes_2006}. %B: this was rephrased.
This system of RNase-based SI is regarded as ancestral in eudicots \citep{igic_2001,steinbachs_2002}, and it is expressed in all SI species of Solanaceae examined to date.
The consequent absence of SI polyploids in this family yields a strong correlation between ploidy and breeding system \citep{robertson_2011}.

@@

Our macroevolutionary analyses in Solanaceae apply different combinations of these techniques in order to parse out the associations of ploidy and breeding system on speciation and extinction rates, while simultaneously allowing that other processes could influence diversification as well.
% separate the associations of lineage diversification rates with breeding system alone, ploidy alone, the interaction between breeding system and ploidy, and additional unobserved factors.
% Here, we examine the roles of ploidy and breeding system, as well as their interaction, on the diversification process in Solanaceae.
% Importantly, our analyses aim to parse out the associations of these two traits on speciation and extinction rates while simultaneously allowing that other processes could influence diversification as well.
We first present models in which the effect of ploidy and breeding system are considered separately, and we compare the inferences to previously published results. 
Then we add a hidden trait to each of those models and investigate whether the focal trait still explains differences in diversification.
Finally, we model ploidy and breeding system jointly to assess their combined relationship to diversification, with or without an additional hidden trait.
With this joint trait model, we also quantify the relative contributions of the two pathways from SI diploids to SC polyploids.
For all of the models involving ploidy, we investigate the potential effects of including diploidization.
Our results highlight the importance of considering non-additive effects of traits on net diversification rates, especially when there are strong biologically-driven correlations among them.

>>>>

Species accumulate across the tree of life at different rates. 
One possible explanation for this phenomenon is that the various traits or character states of species differentially affect rates of diversification. 
Dramatic increases in phylogenetic and phenotypic data and methodological advances have greatly accelerated the search for traits that influence diversification traits.
Nevertheless, identifying focal traits associated with rates of speciation and extinction remains a challenge \citep[\eg][]{maddison_2015, rabosky_2015, beaulieu_2016, rabosky_2017}. 
One difficulty is that speciation and extinction likely do not depend on a single trait, so the biological and environmental contexts in which traits occur can lead to complex interactions that affect lineage diversification \citep{beaulieu_2016, caetano_2018, herrera_2018}.
Consequently, examining the association of only one trait with diversification patterns can be misleading. 
Here, we embrace this challenge by jointly investigating two traits thought to influence speciation and extinction rates---ploidy level and breeding system---while allowing for their interactions and other confounding factors.
% E: We need a "Here, we..." here.  Otherwise, we've just told the reader "not one trait!" and then launch into one trait.
% Could also state that we newly test whether adding one more trait is worthwhile.

Polyploidization is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
The widespread prevalence of variation in ploidy has long been considered a salient feature of flowering plant lineages \citep{stebbins1938}. 
Increase in ploidy can alter many traits and affect a variety of evolutionary and ecological processes \citep{ramsey_2002, sessa_2019}.
%
Polyploids have been documented to have an overall lower diversification rate than diploids \citep{mayrose_2011, mayrose_2015}. 
Other studies, however, find common and numerous paleo-polyploidizations, including some preceding the emergence of highly diverse plant clades \citep{soltis_2014, landis_2018}, suggesting that whole genome duplications have played an important macroevolutionary role driving innovation and diversification in plants. 
Evidence of paleo-polyploidy within the genomes of diploid extant plants also implies pervasive diploidization, the return of polyploids to the diploid state, throughout the angiosperm phylogeny \citep{soltis_2015, dodsworth_2015}.
Our analyses re-examine the association between ploidy and lineage diversification by extending the approach of \citet{mayrose_2011, mayrose_2015} to include these additional processes.
We allow for transitions not only toward polyploidy, but also away from it.
We also allow for heterogeneous diversification within each ploidy level, which could capture, for example, if diploids with a past history of polyploidy diversify more rapidly than diploids with no polyploid ancestry.

@@

Polyploidy and self-fertilization are widely observed to be associated \citep{stebbins1950}.
There are several possible general explanations: whole genome duplication may facilitate the transition to selfing by masking inbreeding depression, self-fertilization may facilitate polyploidy establishment by avoiding the triploid bridge, or both selfing and polyploidy may tend to be found in weedy or peripheral populations \citep{ramsey_1998, barringer2007, barrett2008, husband2008}.
Additionally, in RNase-based gametophytic SI systems, polyploidization alone directly causes the loss of SI \citep{stout1942, lewis1947}. %B: disclaimer: ceteris paribus statement omitted; polyploidization ordinarily causes SC because of the formation of heterodiploid pollen. On the background of deletion of S-locus, or with heterologous chromosome homozygosity at the S-locus may not do so. These, however, appear to be sufficiently rare that they are recovered perhaps twice in dicots: once (or twice) naturally, in sour cherry and its close relative (Prunus), and once in a experimentally induced and selected synthetic pentaploid Solanum (which has not been replicated). Strictly speaking, this is a feature of non-self recognition systems of the kind found in RNase-based GSI.
In these systems, self-incompatibility occurs because haploid self-pollen grains, with one S-allele at the locus controlling the SI response, are unable to detoxify the S-RNase produced by the same S-allele in the style \citep{kubo2010}.
The unreduced pollen of diploids, however, can contain two S-alleles expressed in pollen, which jointly gain the ability to detoxify the S-RNases produced by any maternal genotype \citep{entani1999, tsukamoto2005, kubo2010}.
Initial mutant individuals with pollen containing doubled haploid genomes are consequently capable of self-fertilization, with exceedingly few exceptions \citep{hauck_2002, nunes_2006}.
This system of RNase-based SI is regarded as ancestral in eudicots \citep{igic_2001,steinbachs_2002}, and it is expressed in all SI species of Solanaceae examined to date.
The consequent absence of SI polyploids in this family yields a strong correlation between ploidy and breeding system \citep{robertson_2011}.

@@

Our macroevolutionary analyses in Solanaceae apply different combinations of these techniques in order to parse out the associations of ploidy and breeding system on speciation and extinction rates, while simultaneously allowing that other processes could influence diversification as well.
We first present models in which the effect of ploidy and breeding system are considered separately, and we compare the inferences to previously published results. 
Then we add a hidden trait to each of those models and investigate whether the focal trait still explains differences in diversification.
Finally, we model ploidy and breeding system jointly to assess their combined relationship to diversification, with or without an additional hidden trait.
% E: say something here about testing whether it's worth adding in another real trait?
With this joint trait model, we also quantify the relative contributions of the two pathways from SI diploids to SC polyploids.
For all of the models involving ploidy, we investigate the potential effects of including diploidization.
Our results highlight the importance of considering non-additive effects of traits on net diversification rates, especially when there are strong biologically-driven correlations among them.

### 2019-07-09 manuscript/methods.tex
updated some text for the additional models

%B: IMO: The data subsection would be better organized with parts, (1) ploidy, (2) breeding system, (3) tree, (4) models, (5) model selection and statistical inference.
% E: I changed the subsectioning, but to a different arrangement: (1) Data, (2) Models, (3) Statistical inference, with subsubsections as necessary.

@@

Matching our character state data to the largest time-calibrated phylogeny of Solanaceae \citep{sarkinen_2013} yielded 595 species with ploidy and/or breeding system information on the tree.
% FIXME: update numbers around here
Of these, 290 had information for both states.
The number of species in each combination of states is summarized in \cref{figure:stateclassifications}A.
We retained all 595 species in each of the analyses below because pruning away tips lacking breeding system in the ploidy-only analyses (and vice versa) would discard data that could inform the diversification models.
A total of 405 taxa without any information about breeding system or ploidy were excluded.
%Tips without trait data might not improve point estimation of diversification parameters while increasing uncertainty in the estimates of trait linked diversification
% R-This is very important but I have removed it because I think it is a full on paper by its own
%Including this many more species would have prohibitively slowed our analyses, especially those implementing the most complex models.

@@

Our second model addressed diversification due to ploidy differences while also parsing out heterogeneity of diversification rates due another factor, accommodated by adding a hidden state \citep[HiSSE,][]{beaulieu_2016}. %B: inserted "(trait)", because that seems to be the goal - a biological explanation?  E: I would say hisse captures some factor that evolves like a binary trait, not necessarily a real biological trait
In this model, each of the observed diploid and polyploid states were subdivided by a binary hidden trait with states $A$ and $B$.
In this $D/P+A/B$ ploidy and hidden state model, parameters include speciation rates ($\lambda_{D_A},\ \lambda_{D_B},\ \lambda_{P_A},\ \lambda_{P_B}$) and extinction rates ($\mu_{D_A},\ \mu_{D_B},\ \mu_{P_A},\ \mu_{P_B}$) for each subdivided state.
The polyploidization rate is again represented by $\rho$, and the rates of transition between hidden states are symmetrical with parameter $\alpha$.  % FIXME ?

Diagrams of these two ploidy models are shown in \cref{figure:netdivall}AB.  % request from referee 2

@@

To parse out the effect of breeding system on diversification while allowing for the possibility of heterogeneous diversification rates unrelated to breeding system, we subdivided each of the breeding system states into hidden states $A$ and $B$.
This $I/C+A/B$ breeding system and hidden state model has parameters for state-specific speciation ($\lambda_{I_A},\ \lambda_{I_B},\ \lambda_{C_A},\ \lambda_{C_B}$) and extinction ($\mu_{I_A},\ \mu_{I_B},\ \mu_{C_A},\ \mu_{C_B}$), for loss of SI ($q_{IC}$), and for transitions between hidden states ($\alpha$).
An similar model was used by \citet{freyman_2017} used to study diversification in Onagraceae, but here we restricted the hidden state transitions to be symmetrical. % FIXME still true?

@@

Diagrams of these two breeding system models are shown in \cref{figure:netdivall}CD.  % request from referee 2

@@

Ploidy and breeding system might influence lineage diversification individually, but these two traits also have an intricate association (see the Introduction).
Therefore, we considered a multi-state model that investigates the contribution of both traits and the allowable transitions between them.
This $ID/CD/CP$ ploidy and breeding system model has states for self-incompatible diploids $(ID)$, self-compatible diploids $(CD)$, and self-compatible polyploids $(CP)$; self-incompatible polyploids do not occur, as explained in the Introduction.
There are six parameters for state-specific diversification rates ($\lambda_{ID},\ \lambda_{CD},\ \lambda_{CP}$ for speciation; $\mu_{ID},\ \mu_{CD},\ \mu_{CP}$ for extinction) and three for transitions between states ($\rho_I,\ \rho_C$ for polyploidization transitions from $ID$ and $CD$ to $CP$, respectively; $q_{IC}$ for loss of self-incompatibility without polyploidization, from $ID$ to $CD$).
The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.

Although the $ID/CD/CP$ model allows for two traits to potentially influence diversification, other unknown factors could as well.
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018, huang_2018}.
A fully parameterized version of this $ID/CD/CP+A/B$ model would have 26 rate parameters. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fit a simplified version with 16 parameters.
% FIXME still true?
The reduction in parameter space was achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\rho_C,\ q_{IC}$ as defined for the $ID/CD/CP$ model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},  \lambda_{ID_B},  \lambda_{CD_A}, \lambda_{CD_B}, \lambda_{CP_A}, \lambda_{CP_B}, \mu_{ID_A}, \mu_{ID_B}, \mu_{CD_A}, \mu_{CD_B},  \mu_{CP_A}, \mu_{CP_B}$).
%B: I can't tell, but it seems to me that this 26->16 parameter reduction makes it possible to underestimate the effect of these hidden states.Perhaps this complication is covered in the Discussion section. 
%R- It is possible, but adding all the parameters can also result in an underestimation of the hidden states contribution because it is not enough sample to accurately estimate transitions. In my simulations for diversification-free models, accurately estimating 10 parameters can only be achieved with trees with more than 500 tips. Because of that experience I think 16 parameters is already pushing really the inference machine hard. This happens because the phylogeny is not an independent sample so your ESS is much much smaller and you might end up over-parameterizing.

Diagrams of these two ploidy and breeding system models are shown in \cref{figure:netdivall}EF.  % request from referee 2

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states} % FIXME: update numbers
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known.
(A) The five categories and the number of species in each.
Abbreviations are $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, SI species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC.
(B) Category groupings into states for each model type.
For example, there are 34 species that are SC with unknown ploidy. % FIXME: update number if necessary
In the $D/P$ models these are coded as either $D$ or $P$ (uncertain/consistent with either state), in the $I/C$ models they are coded as $C$, and in the ID/CD/CP models they are coded as either $CD$ or $CP$.
In the hidden state models, all species were coded as consistent with both $A$ and $B$.
}
\label{figure:stateclassifications}
\end{figure}

>>>>

%B: IMO: The data subsection would be better organized with parts, (1) ploidy, (2) breeding system, (3) tree, (4) models, (5) model selection and statistical inference.
% E: I changed the subsectioning, but to a different arrangement: (1) Data, (2) Models, (3) Statistical inference.  With subsubsections as necessary.

@@

Matching our character state data to the largest time-calibrated phylogeny of Solanaceae \citep{sarkinen_2013} yielded 595 species with ploidy and/or breeding system information on the tree.
% FIXME: Rosana will update numbers around here
Of these, 290 had information for both states.
The number of species in each combination of states is summarized in \cref{figure:stateclassifications}A.
We retained all 595 species in each of the analyses below because pruning away tips lacking breeding system in the ploidy-only analyses (and vice versa) would discard data that could inform the diversification models.
A total of 405 taxa without any information about breeding system or ploidy were excluded.
%Tips without trait data might not improve point estimation of diversification parameters while increasing uncertainty in the estimates of trait linked diversification
% R-This is very important but I have removed it because I think it is a full on paper by its own
%Including this many more species would have prohibitively slowed our analyses, especially those implementing the most complex models.

@@

To address diversification due to ploidy differences while also parsing out heterogeneity of diversification rates due another factor, we used models that include a hidden state \citep[HiSSE,][]{beaulieu_2016}. %B: inserted "(trait)", because that seems to be the goal - a biological explanation?  E: I would say hisse captures some factor that evolves like a binary trait, not necessarily a real biological trait
In these models, the observed diploid and polyploid states were each subdivided by a binary hidden trait with states $A$ and $B$.
In these $D/P+A/B$ ploidy and hidden state models, parameters include speciation rates ($\lambda_{D_A},\ \lambda_{D_B},\ \lambda_{P_A},\ \lambda_{P_B}$) and extinction rates ($\mu_{D_A},\ \mu_{D_B},\ \mu_{P_A},\ \mu_{P_B}$) for each subdivided state.
In the simplest case, the polyploidization rate, $\rho$, is the same within each hidden state, and the rates of transition between hidden states are symmetrical with parameter $\alpha$.
We also considered the more complex cases with different polyploidization rates in each hidden state ($\rho_A$ and $\rho_B$) and asymmetric transitions between hidden states ($\alpha$ and $\beta$).

% E: Rosana, please check this paragraph.  Did I get it correct?
To test if diversification rate heterogeneity is due only to a hidden trait and not the ploidy trait, we used character-independent diversification models \citep[CID,][]{beaulieu_2016}.
Parameters in this case are speciation and extinction rates for the hidden states ($\lambda_A,\ \lambda_B,\ \mu_A,\ \mu_B$), along with polyploidization ($\rho$) and transitions between hidden states ($\alpha$).

Diagrams of these ploidy models are shown in \cref{figure:netdivall}AB.  % request from referee 2
% FIXME: ref to additional D/P models

@@

To parse out the effect of breeding system on diversification while allowing for the possibility of heterogeneous diversification rates unrelated to breeding system, we subdivided each of the breeding system states into hidden states $A$ and $B$.
This $I/C+A/B$ breeding system and hidden state model has parameters for state-specific speciation ($\lambda_{I_A},\ \lambda_{I_B},\ \lambda_{C_A},\ \lambda_{C_B}$) and extinction ($\mu_{I_A},\ \mu_{I_B},\ \mu_{C_A},\ \mu_{C_B}$), for loss of SI ($q_{IC}$), and for transitions between hidden states ($\alpha$).
We also considered more complex models with different transition rates in each hidden state (???) and asymmetric transitions between hidden states ($\alpha$ and $\beta$). % FIXME
Similar models were used by \citet{freyman_2017} used to study diversification in Onagraceae.

% E: Rosana, please check this paragraph.  Did I get it correct?
We further used character-independent diversification models to test if diversification rate heterogeneity is due only to a hidden trait and not the breeding system trait.
Parameters in this case are speciation and extinction rates for the hidden states ($\lambda_A,\ \lambda_B,\ \mu_A,\ \mu_B$), along with loss of SI ($q_{IC}$) and transitions between hidden states ($\alpha$).

@@

Diagrams of these breeding system models are shown in \cref{figure:netdivall}CD.  % request from referee 2
% FIXME: ref to additional I/C models

@@

Ploidy and breeding system might influence lineage diversification individually, but these two traits also have an intricate association (see the Introduction).
Therefore, we considered a multi-state model that investigates the contribution of both traits and the allowable transitions between them.
This $ID/CD/CP$ ploidy and breeding system model has states for self-incompatible diploids $(ID)$, self-compatible diploids $(CD)$, and self-compatible polyploids $(CP)$; self-incompatible polyploids do not occur, as explained in the Introduction.
There are six parameters for state-specific diversification rates ($\lambda_{ID},\ \lambda_{CD},\ \lambda_{CP}$ for speciation; $\mu_{ID},\ \mu_{CD},\ \mu_{CP}$ for extinction) and three for transitions between states ($\rho_I,\ \rho_C$ for polyploidization transitions from $ID$ and $CD$ to $CP$, respectively; $q_{IC}$ for loss of self-incompatibility without polyploidization, from $ID$ to $CD$).
The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
% E: Can we call it something other than q_IC?  It's a bit confusing to have the same parameter mean different things in different models.

% E: This paragraph is new.  Rosana, please check.
We would like to test whether including an additional trait significantly improves the model fit.
For example, does the model with both breeding system and ploidy provide a significantly better fit than the model with only ploidy?
To answer this, it is not valid to compare the $IC/CD/CP$ and $D/P$ model fits, as defined above, because they use different data.
Similarly, the $IC/CD/CP$ and $I/C$ models cannot be compared statistically.
Instead, we define lumped models \citep{tarasov_2019} that use the state space of the $IC/CD/CP$ model but constrain the rate parameters to mimic the behavior of the single-trait models. % should ref a figure

% E: We now have so many models to describe, I'm feeling like all this text may not be the best way.  I'm wondering if we can rely on figures/tables instead, and only write out the overall strategy.

Although the $ID/CD/CP$ model allows for two traits to potentially influence diversification, other unknown factors could as well.
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018, huang_2018}.
A fully parameterized version of this $ID/CD/CP+A/B$ model would have 26 rate parameters. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fit a simplified version with 16 parameters.
% FIXME Rosana, please update about the parameters
The reduction in parameter space was achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\rho_C,\ q_{IC}$ as defined for the $ID/CD/CP$ model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},  \lambda_{ID_B},  \lambda_{CD_A}, \lambda_{CD_B}, \lambda_{CP_A}, \lambda_{CP_B}, \mu_{ID_A}, \mu_{ID_B}, \mu_{CD_A}, \mu_{CD_B},  \mu_{CP_A}, \mu_{CP_B}$).
%B: I can't tell, but it seems to me that this 26->16 parameter reduction makes it possible to underestimate the effect of these hidden states.Perhaps this complication is covered in the Discussion section. 
%R- It is possible, but adding all the parameters can also result in an underestimation of the hidden states contribution because it is not enough sample to accurately estimate transitions. In my simulations for diversification-free models, accurately estimating 10 parameters can only be achieved with trees with more than 500 tips. Because of that experience I think 16 parameters is already pushing really the inference machine hard. This happens because the phylogeny is not an independent sample so your ESS is much much smaller and you might end up over-parameterizing.

Diagrams of these ploidy and breeding system models are shown in \cref{figure:netdivall}EF.  % request from referee 2
% FIXME: ref to additional models?

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states} % FIXME: update numbers
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known.
(A) The five categories and the number of species in each.
Abbreviations are $I$ for self-incompatible, $C$ for self-compatible, $D$ for diploid, $P$ for polyploid, $?$ for unknown.
Because polyploidization breaks this form of self-incompatibility, SI species with unobserved ploidy ($I?$) are taken to be diploid ($ID$), and polyploid species with unobserved breeding system ($?P$) are taken to be SC.
(B) Category groupings into states for each model type.
For example, there are 34 species that are SC with unknown ploidy. % FIXME: update number if necessary
In the $D/P$ models these are coded as either $D$ or $P$ (uncertain/consistent with either state), in the $I/C$ models they are coded as $C$, and in the $ID/CD/CP$ models they are coded as either $CD$ or $CP$.
In the hidden state models, all species were coded as consistent with both $A$ and $B$.
}
\label{figure:stateclassifications}
\end{figure}
